\plaintitle

### 2018-04-01 paper/paper.tex
...

% End of preamble. Here it comes the document.
\begin{document}

@@

  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  \textsf{ExpandHelp} that can be used in a wide area of situations
  where such translation is required.
  We show how our framework can be used
  in the \textsf{GitHelp} system
  with which user can easily generate complex \texttt{git} commands
  from fragments of users' intentions.

@@

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of a ``translation paradigm''
\item IME-like command etnry system
% やりたいことを実行するインタフェース (IME的なもの)
\item Flexible dynamic search system based on RegExp (ExpandHelp)
% そのための柔軟なインフラ (ExpandHelp)
\item Data sharing infrastructure for the translation paradigm
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

@@

We have implemented the ``GitHtlp'' system that can translate
user' intentions into a correct \texttt{git} commands
using the \textsf{ExpandHelp} framework.

@@

We assume that a user is using \texttt{bash} for developing a software system.

When a

@@

When the user wants to compare the latest \texttt{README.md} file with an
older version, he tries to use \texttt{git} to show the difference.
He may know that he can use the \texttt{git diff} command to do the
conparison and invoke the following command,

\begin{quotation}
  \verb|$ git diff README.md|
\end{quotation}

but nothing happens, because this is not the right command
to compare the latest version with older version.
%
More experienced user might use a command like the following,
but it does not show anything either, because
\verb|HEAD^^| means...

@@

Instead, the user can type \texttt{Cmd-Ctrl-G} to invoke
\textsf{GitHelp}
after typing
\texttt{\$ git RE 2}.

\begin{figure}[b]
  \includegraphics[width=8cm,bb=0 0 1290 866]{figures/githelp1.png}
  \caption{Invoking GitHelp.}
  \label{bash1}
\end{figure}

Here, various command strings and descriptions are listed,
one of which says ``.....'',
which means that ``to compare README with two older verson.''
%
If the user thinks that that's what he wanted to do,
he can select the entry by typing arrow keys and
type the enter key.

>>>>

% End of preamble. Here it comes the document.

\def\GH{\textsf{GitHelp}}

\begin{document}

@@

  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  \textsf{ExpandHelp} that can be used in a wide area of situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex \texttt{git} commands
  from fragments of users' intentions.

@@

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of a ``translation paradigm'' to control a machine from vague specifications
\item IME-like command etnry system
% やりたいことを実行するインタフェース (IME的なもの)
\item Flexible dynamic search system based on RegExp (ExpandHelp)
% そのための柔軟なインフラ (ExpandHelp)
\item Data sharing infrastructure for the translation paradigm
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

@@

We have implemented the \textsf{GitHtlp} system
with which a user can translate his vague intention in various languages
into a complete \texttt{git} commands
using the \textsf{ExpandHelp} framework.

@@

We assume that the user is using \texttt{bash} for his software
development activities.

@@

When the user wants to compare the latest \texttt{README.md} file with an
older version, he tries to use \texttt{git} to show the difference.
He may know that he can use the \texttt{git diff} command to do the
conparison and invoke the following command like the following.

\begin{quotation}
  \begin{verbatim}
    $ git diff README.md
    $
  \end{verbatim}
\end{quotation}

Nothing happens, because this is not the right command
to compare the latest version with older version.
%
More experienced user might use a command like the following,
but it does not show anything either, because the version specification
``\verb|HEAD^^|''
points at a file included in the older ``commit'',
and

@@

If {\GH} is installed,
the user can type a special key (e.g. \texttt{Cmd-Ctrl-G}) to invoke {\GH}
after typing ``\texttt{git RE 2}''.

\begin{figure}[b]
  \includegraphics[width=8cm,bb=0 0 1290 866]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash1}
\end{figure}

Here, various candidate entries with
descriptios and command strings are listed.
One of the entries says ``.....'',
which means that ``to compare README with two older verson.''
%
If the user thinks that that's what he wanted to do,
he can select the entry by typing arrow keys and
type the enter key.
